---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(equatags)
```

# equatags

<!-- badges: start -->
[![R build status](https://github.com/ardata-fr/equatags/workflows/R-CMD-check/badge.svg)](https://github.com/ardata-fr/equatags/actions)
<!-- badges: end -->

The goal of the package is to provide a tool to transform latex math expressions
into `HTML` format and `Office Open XML Math` format (which can be used in a
Word or PowerPoint document). 


## Installation

You can install the development version from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("davidgohel/equatags")
```

## Example with flextable


```{r eval=FALSE}
library(flextable)

eqs <- c(
  "(ax^2 + bx + c = 0)",
  "a \\ne 0",
  "x = {-b \\pm \\sqrt{b^2-4ac} \\over 2a}")
df <- data.frame(formula = eqs)
df


ft <- flextable(df)
ft <- compose(
  x = ft, j = "formula",
  value = as_paragraph(as_equation(formula)))
ft <- align(ft, align = "center", part = "all")
ft <- width(ft, width = 2, j = "formula")
ft
```


## Related work

* Packages [texPreview](https://CRAN.R-project.org/package=texPreview) written by 
Jonathan Sidi, "compile snippets of 'LaTeX' directly into 
images from the R console to view in the 'RStudio' viewer pane, Shiny apps 
and 'RMarkdown' documents". With this package, you can get images from 
your 'latex' code. The tool offers a wider functional spectrum than just 
equation processing and focuses on 'latex' instead of only 'MathJax' equations.

* Package [mathjaxr](https://cran.r-project.org/package=mathjaxr) written by 
Wolfgang Viechtbauer, "Using 'Mathjax' in Rd Files". This package let you 
add equations in the manual pages of your package in a very convenient way. 

* Package [katex](https://cran.r-project.org/package=katex) written by 
Jeroen Ooms, "Rendering Math to HTML, 'MathML', or R-Documentation Format". 
'equatags' mainly uses its functions since the release of 'katex' that made 
possible to get rid of node.js dependancy.
