---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(locatexec)
library(equatags)
```

# equatags

<!-- badges: start -->
[![R build status](https://github.com/davidgohel/equatags/workflows/R-CMD-check/badge.svg)](https://github.com/davidgohel/equatags/actions)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

The goal of the package is to provide a tool to transform equations expressed in
`latex`, `MathML` or `ASCIIMathML` into `SVG` format (i.e. as an image) and
`Office Open XML Math` format (which can be used in a Word or PowerPoint
document).

## Installation

You can install the development version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("davidgohel/equatags")
```
## Example

```{r eval=(exec_available("node") && mathjax_available())}
library(equatags)
x <- c("(ax^2 + bx + c = 0)",
       "x = {-b \\pm \\sqrt{b^2-4ac} \\over 2a}")
z <- transform_mathjax(x = x, to = "svg")

writeLines(z[1], "man/figures/eq1.svg", useBytes = TRUE)
writeLines(z[2], "man/figures/eq2.svg", useBytes = TRUE)
```

![equation 1](man/figures/eq1.svg)

![equation 2](man/figures/eq2.svg)
